\chapter{Abstract}

Computer-aided art design such as computer painting, computer automatic coloring, etc. has long been a problem that researchers have long explored, because it is related to the diversity of human expression and the complexity of human experience make it a challenging task which was strongly and continuously explorated by scientists. 
With the development of artificial intelligence and machine learning in recent years, there has been a new breakthrough in computer art aid systems. For example, GAN can automatically produce pictures, pixel2pixel can automatically fill colors according to existing styles, and PaintsChainer can provide The secondary meta picture is automatically colored.

This paper presents an automatic color palettes generator and coloring system based on semantic intelligence understanding. 
The system mainly solves that the current automatic coloring system can only  color by labels or relying on existing color styles migration, thereby making the system more intelligent and responding directly to human language. 
For designers, this system can instantly convert the description of the text into color palettes and color the sketch, which greatly facilitates its convenience. The color palettes comes from artworks and has a unique aesthetic that can help designers.

This paper uses three innovations to solve this problem: 1. Using a deep learning model to understand the semantics; 2. Correlating picture information with hidden information at the semantic level, and the partiality characteristics of the picture style similarity are preserved to its partial description of semantic description; 3. In this paper, Flood Fill Algorithm and Random Walk are used to automatically fill in the image.

There are four difficulties in solving the text: 1. To Use word2vect to semantically understand the text and artwork of the input text, and to design the coding format with semantic information. 2. To compare the coding information of the input text and the coded information of the artworks，and  to search for the artwork with the closest distance; 3. Extraction of color features of artworks; 4. A series of problems in coloring: color continuity, color ratio, and light and shadow effects of the effect map.

This algorithm has achieved good results in the actual testing of interior design linear drawings,and has achieved the best results in the industry.

{
    \vspace{1em}
    \setlength{\parindent}{0em}
    \textbf{Keywords} \; computer aided design  \; nlp\; representation learning \; deep learning \par
}
